---
title: "report"
date: "`r lubridate::now()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "#>", 
                      warning = FALSE, message = FALSE,
                      dpi = 600)
pacman::p_load(googlesheets, MASS, tidyverse, janitor, filesstrings,
               quantmod, lubridate, magrittr, clipr, knitr, conflicted)

ensure_time_hm <- function(x) {
  if (!is.difftime(x)) x %<>% hm()
  x
}

ensure_date_dmy <- function(x) {
  if (!is.Date(x)) x %<>% dmy()
  x
}

evaluate_frac <- function(x) {
  map_dbl(x, ~ eval(parse(text = .)))
}

get_week <- function(date_vec) {
  date_vec %>% 
    as.numeric() %>% 
    {((. - min(.)) %/% 7) + 1}
}

get_exchange_rate <- function(from, to, dt = Sys.Date()) {
  obj.names <- getFX(paste0(from, "/", to), from = dt - 1, to = dt)
  result <- numeric(length(obj.names))
  names(result) <- obj.names %>% 
    str_replace(coll("/"), "") %>% 
    str_to_upper()
  for (n in names(result)) {
    result[n] <- as.numeric(get(n))[1]
    rm(n)  # cleanup
  }
  return(result)
}

exrate_gbp_eur <- get_exchange_rate("GBP", "EUR")
investments <- c(Rory = 4000, Aidan = 4000, John = 1000)

### Get the spreadsheet
bad <- TRUE
bad_count <- 0
gs_auth(token = readRDS("googlesheets_token.rds"))
while (bad) {
  df <- "Sys Syndo" %>%
  gs_title() %>%
  gs_read("Cat 20") %>%
  clean_names() %>% 
  dplyr::filter(!is.na(date), !is.na(profit_at_time_pts), nchar(result) > 2) %>% 
  mutate(date = ensure_date_dmy(date), 
         time = ensure_time_hm(time),
         result = str_trim(result),
         result = if_else(tolower(result) %in% c("uml", "unl"), 
                          "Unmatched Loss", result),
         result = if_else(tolower(result) %in% c("umw", "unw"), 
                          "Unmatched Win", result)) %>% 
  arrange(date, time, course, horse) %>% 
  rename(eur_pt = "pt", gbp_pt = "pt_2", 
         profit_eur = "profit", profit_gbp = "profit_2") 
  if (is.numeric(df$profit_pts) && is.numeric(df$profit_at_time_pts))
    bad <- FALSE
  if (bad) {
    bad_count <- bad_count + 1
    Sys.sleep(3)
    if (bad_count > 99) stop("Tried and failed to read sheet 100 times.")
  }
}
df_deduped <- df %>% 
  mutate(ew = !is.na(places)) %>% 
  group_by(date, time, course, horse, ew, result) %>% 
  summarise(
    odds = mean(evaluate_frac(odds) * stake_line_pts / sum(stake_line_pts)),
    stake_line_pts = sum(stake_line_pts),
    rule_4 = mean(first_number(rule_4) * profit_pts / sum(profit_pts)) / 100,
    profit_pts = sum(profit_pts)
  ) %>% 
  ungroup() %>% 
  mutate(rule_4 = if_else(is.na(rule_4), 0, rule_4))

eur_pt_change_dates <- df %>% 
  dplyr::filter(c(FALSE, diff(eur_pt) != 0)) %>% 
  dplyr::pull(date)
payment_dates <- c(df$date[1], eur_pt_change_dates)
```

# Profit over time

```{r profit-over-time}
plot_df <- df %>% 
  mutate(week = get_week(date)) %>% 
  group_by(week) %>% 
  summarise(pat = median(profit_at_time_pts)) 
plot_df %<>% bind_rows(
  tibble(week = dplyr::last(.[["week"]] + 1), 
         pat = dplyr::last(df$profit_at_time_pts))
  )
x_breaks <- seq(0, max(plot_df$week) + 9, by = 10)
y_breaks <- 0
while (max(plot_df$pat) > max(y_breaks)) y_breaks %<>% c(max(y_breaks) + 20)
while (min(plot_df$pat) < min(y_breaks)) y_breaks %<>% c(min(y_breaks) - 20)
ggplot(plot_df, aes(x = week, y = pat)) + 
  geom_hline(yintercept = 0, colour = "red") + geom_line() + 
  ylab("profit at time (pts)") + ggtitle("profit over time") +
  scale_x_continuous(breaks = x_breaks) +
  scale_y_continuous(breaks = y_breaks)
```

```{r profit-over-time-smooth}
ggplot(plot_df, aes(x = week, y = pat)) + 
  geom_hline(yintercept = 0, colour = "red") + geom_smooth(se = FALSE) + 
  ylab("profit at time (pts)") + ggtitle("smoothed profit over time") +
  scale_x_continuous(breaks = x_breaks) +
  scale_y_continuous(breaks = y_breaks)
```


# ROI and ROC

```{r end-profit, include=FALSE}
profit_df <- df %>% 
  dplyr::filter(!is.na(date)) %>% 
  mutate(profit_gbp = as.numeric(str_replace_all(profit_gbp, "£", "")), 
         profit_eur = as.numeric(str_replace_all(profit_eur, "€", "")))
profit_eur <- sum(as.numeric(profit_df$profit_eur)) + 
  sum(as.numeric(profit_df$profit_gbp)) * exrate_gbp_eur
profit_eur %<>% round()
total_fee_eur <- 3 * 600 * exrate_gbp_eur
total_fee_eur %<>% round()
point_eur_mean <- mean(profit_df$eur_pt)
wagered_total_eur <- profit_df %>% 
  mutate(w_t = if_else(is.na(places), stake_line_pts,
                       2 * stake_line_pts)) %>% 
  dplyr::pull(w_t) %>% 
  sum() %>% 
  c(point_eur_mean) %>% 
  prod() %>% 
  round()
total_investment_eur <- 9000
```

We put in €`r total_investment_eur` and we've made a profit of €`r format(profit_eur, sci = FALSE, big.mark = ",")` on the bets. However, we've paid three subscriptions of £600 which amounts to €`r format(total_fee_eur, sci = FALSE, big.mark = ",")` so our net profit is €`r format(profit_eur - total_fee_eur, sci = FALSE, big.mark = ",")`. That's a return on capital of `r round(100 * (profit_eur - total_fee_eur) / total_investment_eur, 2)`%. This gives us a current bank of €`r format(round(total_investment_eur - total_fee_eur + profit_eur), sci = FALSE)`.

We have wagered a total of €`r format(wagered_total_eur, big.mark = ",")` and made a betting profit of €`r format(profit_eur, sci = FALSE, big.mark = ",")`, which gives us a betting ROI of `r round(100 * profit_eur / wagered_total_eur, 2)`%.


# Have any bookies been riddled?

```{r bookies}
nas_to_zero <- function(x) {
  x[is.na(x)] <- 0
  x
}

pos_to_plus <- function(x) {
  pos <- x > 0
  prefix <- if_else(pos, "+", "")
  str_c(prefix, x)
}

df %>% 
  group_by(placer, bookmaker) %>% 
  summarise(profit_pts = sum(profit_pts)) %>% 
  ungroup() %>% 
  spread(placer, profit_pts) %>%
  mutate_if(is.numeric, nas_to_zero) %>%
  mutate(total = Aidan + Rory) %>% 
  arrange(desc(total)) %>% 
  mutate_if(is.numeric, round) %>% 
  mutate_if(is.numeric, pos_to_plus) %>% 
  kable()
```


# Minimum acceptable odds

```{r min-acceptable-odds}
winnings_sum <- df$profit_pts %>% {sum(.[. > 0])} %>% round()
losses_sum <- df$profit_pts %>% {-sum(.[. < 0])} %>% round()
profit_factor <- losses_sum / winnings_sum
```

We've had winnings of `r winnings_sum` points and losses of `r losses_sum` points, so even if our odds were only a fraction `r losses_sum` / `r winnings_sum` = `r round(losses_sum / winnings_sum, 2)` of what we actually got, we'd still be breaking even.


# Winners and losers

Here's a count of the number of winners, losers, and places we've had.

```{r winners-losers-count}
df_win_lose <- df %>% 
  mutate(ewres = paste(if_else(is.na(places), "Win only", "Each way"),
                       result)) %>% 
  dplyr::pull(ewres) %>% {
    .[!str_detect(., "NR")]
  } %>% 
  tabyl() %T>% 
  {names(.)[1] <- "result"} %>% 
  arrange(desc(n)) %>% 
  mutate(percent = str_c(round(percent * 100), "%"))
kable(df_win_lose)
```


# Win only vs each way

```{r win-ew}
win_total_eur <- profit_df %>% 
  dplyr::filter(is.na(places)) %>% 
  mutate(prof_eur = profit_eur + profit_gbp * exrate_gbp_eur) %>% 
  dplyr::pull(prof_eur) %>% 
  sum() %>% 
  round()
ew_total_eur <- profit_df %>% 
  dplyr::filter(!is.na(places)) %>% 
  mutate(prof_eur = profit_eur + profit_gbp * exrate_gbp_eur) %>% 
  dplyr::pull(prof_eur) %>% 
  sum() %>% 
  round()
non_dup_bets <- dplyr::filter(df, !duplicated(paste(date, horse)))
n_win_bets <- sum(is.na(non_dup_bets$places))
n_ew_bets <- sum(!is.na(non_dup_bets$places))
```

* We've made `r n_win_bets` _win only_ bets, on which we've made a profit of €`r format(win_total_eur, big.mark = ",")`. 
* We've made `r n_ew_bets` _each way_ bets, on which we've made a profit of €`r format(ew_total_eur, big.mark = ",")`.


# Unmatched Bets

```{r prepare-unmatched}
df_deduped_winonly <- dplyr::filter(df_deduped, !ew)
n_matched_winners <- df_deduped_winonly %>% 
  dplyr::filter(result == "Win") %>% 
  nrow()
n_matched_losers <- df_deduped_winonly %>% 
  dplyr::filter(result == "Lose") %>% 
  nrow()
matched_win_perc <- 
  round(n_matched_winners / (n_matched_losers + n_matched_winners) * 100)
n_unmatched_winners <- df_deduped_winonly %>% 
  dplyr::filter(result == "Unmatched Win") %>% 
  nrow()
n_unmatched_losers <- df_deduped_winonly %>% 
  dplyr::filter(result == "Unmatched Loss") %>% 
  nrow()
unmatched_win_perc <- 
  round(n_unmatched_winners / (n_unmatched_losers + n_unmatched_winners) * 100)
mean_rule4 <- df_deduped_winonly %>% 
  dplyr::filter(!str_detect(result, "Unmatched")) %>% 
  dplyr::filter(str_detect(result, "Win")) %>% 
  dplyr::pull(rule_4) %>% 
  mean()
pts_saved_by_unmatched <- df_deduped_winonly %>% 
  dplyr::filter(result == "Unmatched Loss") %>% 
  dplyr::pull(stake_line_pts) %>% 
  sum() %>% 
  round()
pts_lost_by_unmatched <- df_deduped_winonly %>% 
  dplyr::filter(result == "Unmatched Win") %>% 
  mutate(missed = stake_line_pts * odds) %>% 
  dplyr::pull(missed) %>% 
  sum() %>% 
  prod(1 - mean_rule4, 0.8) %>% 
  round()
pts_gained_by_better_posted_odds <- df %>% 
  dplyr::filter(date >= "2018-09-01",
         str_detect(bookmaker, "atchbook"),
         profit_pts > 0) %>% 
  dplyr::pull(profit_pts) %>% 
  sum() %>% 
  prod(1 / 0.8 - 1) %>% 
  round()
pts_profit_by_unmatched <- pts_saved_by_unmatched - pts_lost_by_unmatched +
  pts_gained_by_better_posted_odds
unmatched_desc <- if_else(pts_profit_by_unmatched >= 0, "saved", "cost")
```

We'll consider only win only bets (and not each way bets) in this section.

Of the bets that have been matched, there have been `r n_matched_winners` winners and `r n_matched_losers` losers. That means that `r matched_win_perc`% of matched bets have been winners. Of the bets that have not been matched, there have been `r n_unmatched_winners` winners and `r n_unmatched_losers` losers. That means that `r unmatched_win_perc`% of unmatched bets have been winners. Unmatched bets have saved us `r pts_saved_by_unmatched` points on losers but cost us `r pts_lost_by_unmatched` on winners, whereas getting better odds on posted bets which were matched has made us `r pts_gained_by_better_posted_odds` points (where I have assumed that when we post, we get 20% better odds than if we'd just taken best available at the time). So overall, choosing to post when we do (rather than taking the bad bbest available odds) has `r unmatched_desc` us `r abs(pts_profit_by_unmatched)` points.
